---
title: "Clustering of cognition-perception-ability verses"
author: "Anna Sjöberg"
output: 
  html_document:
    theme: paper
    include:
      after_body: footer.html
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(ggiraph)
library(shiny)
```

---

### Explore the clustering
In the plot below, you can explore the clustering at different number of clusters. Pick the number of clusters in the drop-down menu. Each point represents a verse in the verse sample, and the colour represents the clustering at 10 clusters (as discussed in section 5.4 of *Knowledge predication*). Hover over a point to read the verse it represents.

<iframe height="600" width="100%" frameborder="no" src="https://annasjob.shinyapps.io/viewClusters/"> </iframe>

### The clusters
```{r, echo=FALSE}
library(DT)
df<-read.table("clusters.csv", sep="\t", header=T, encoding="UTF-8")
df <- df[, c("Named8", "Named10", "Verse", "Text", "N2", "N3", "N4", "N5", "N6", "N7", "N8", "N9", "N10")]

datatable(data=df, rownames=FALSE, extensions = 'Buttons', options = list(dom = 'Bfrtip', columnDefs = list(list(visible=FALSE, targets=c(1,4,5,6,7,8,9,10, 11, 12))), buttons = list(list(extend = 'colvis', columns = c(0,1,4, 5,6,7,8,9,10, 11, 12)))))
```
### Download
<a href="clusters.csv" download>Download the full clustering</a>

