---
title: "The Dimensions of Knowledge Predication"
author: "Anna Sjöberg"
output: 
  html_document:
    theme: paper
    include:
      after_body: footer.html
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(ggiraph)
library(shiny)
```

---
This page presents the dimensions of knowledge predication as found by a CMDS analysis, the details of which I present in chapter 7 of *Knowledge predication*. 

### Explore the dimensions
The dimensions of the CMDS analysis can be explored in the plot below. Use the drop-down menus to change which dimensions and which language are displayed. Hover over a point to read the verse it represents. 

<iframe height="600" width="100%" frameborder="no" src="https://annasjob.shinyapps.io/viewDimensions/"> </iframe>
```{r tabsets, echo=FALSE} 


```

### Table of verses with dimensions
Below is a table of the verses in the extended knowledge domain and their values in the six dimensions analysed in *Knowledge predication*. 

```{r, echo=FALSE}
library(DT)
df<-read.table("dimensions2.csv", sep=";", header=T, encoding="UTF-8")
df$Dimension1 <- round(df$Dimension1, 3)
df$Dimension2 <- round(df$Dimension2, 3)
df$Dimension3 <- round(df$Dimension3, 3)
df$Dimension4 <- round(df$Dimension4, 3)
df$Dimension5 <- round(df$Dimension5, 3)
df$Dimension6 <- round(df$Dimension6, 3)

datatable(data=df, rownames=FALSE, extensions = 'Buttons', options = list(dom = 'Bfrtip', columnDefs = list(list(visible=FALSE, targets=c(4,5,6,7,8))), buttons = list(list(extend = 'colvis', columns = c(3,4,5,6,7,8)))))

```

### Download
<a href="dimensions2.csv" download>Download the verses with values on dimensions</a>