---
title: "Languages"
output:
  html_document:
    theme: paper
    include:
      after_body: footer.html
    toc: true
    toc_depth: 5
    toc_float: true
---
---

```{r setup, include=FALSE}
library(DT)
library(lingtypology)
library(pandoc)
knitr::opts_chunk$set(echo = FALSE)
df <- read.csv("constructions.csv", header=T, sep="\t", encoding="UTF-8")
df_lngs <- read.csv("languages.csv", sep=";")

```

### North and Meso-America
```{r}
df_lngsb <- df_lngs[which(df_lngs$area =="North America"),]
map.feature(languages = lang.iso(df_lngsb$lng),
            features = df_lngsb$Type,
            label = lang.iso(df_lngsb$lng),
            popup = lang.iso(df_lngsb$lng)
            )
```

#### Bribri (bzd)
Bribri is a Chibchan language spoken by approximately 7000 people.

The principal constructions for expressing knowledge predication in the Briri New Testament are found in the table below.  

```{r}
df_sub <- df[which(df$Language == "bzd"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

#### Comaltepec Chinantec (cco)
Comaltepec Chinantec is a Western Otomanguean language spoken by approximately 2 000 people.

The principal constructions for expressing knowledge predication in the Chinantec New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "cco"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

#### Cherokee (chr)
Cherokee is an Iroquoian language spoken by approximately 1 520 people.

The principal constructions for expressing knowledge predication in the Cherokee New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "chr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
#### Chol (ctu)
Chol is a Mayan language spoken by approximately 252 000 people.

The principal constructions for expressing knowledge predication in the Chol New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "ctu"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
#### Nopala Chatino (cya)
Nopala Chatino is an Eastern Otomanguean language spoken by approximately 8 940 people.

The principal constructions for expressing knowledge predication in the Chatino Nopala New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "cya"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
#### Dogrib (dgr)
Dogrib is an Athabaskan-Eyak-Tlingit language spoken by approximately 1 650 people.

The principal constructions for expressing knowledge predication in the Dogrib New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "dgr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
#### Central Alaskan Yupik (esu)
Central Alaskan Yupik is an Eskimo-Aleut language spoken by about 10 000 people.

The principal constructions for expressing knowledge predication in the Central Alaskan Yupik New Testament are found in the table below.

```{r}
df_sub <- df[which(df$Language == "esu"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Hopi (hop)
Hopi is a Northern Uto-Aztecan language spoken by around 6 080 people.

The principal constructions expressing knowledge predication in the Hopi New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "hop"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Tol (Jicaque) (jic)
Tol (Jicaque) is a Jicaquean language spoken by around 300 people.

The principal constructions expressing knowledge predication in the Tol (Jicaque) New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "jic"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

##### Mi'kmaq (mic)
Mi'kmaq is an Algic language spoken by around 6 900 people.

The principal constructions expressing knowledge predication in the Mi'kmaq New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mic"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Mixe (mxp)
Mixe is a Mixe-Zoque language spoken by around 16 800 people.

The principal constructions expressing knowledge predication in the Mixe New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mxp"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Pennsylvania German (pdc)
Pennsylvania German is an Indo-European>Germanic/Creole language spoken by around 148 000 people.

The principal constructions expressing knowledge predication in the Pennsylvania German New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "pdc"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Purepecha (pua)
Purepecha is a Tarascan language spoken by around 180 000 people.

The principal constructions expressing knowledge predication in the Purepecha New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "pua"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Tlachichilco Tepehua (tpt)
Tlachichilco Tepehua is a Totonacan language spoken by around 3 000 people.

The principal constructions expressing knowledge predication in the Tlachichilco Tepehua New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "tpt"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
### South America
```{r}
df_lngsb <- df_lngs[which(df_lngs$area =="South America"),]
map.feature(languages = lang.iso(df_lngsb$lng),
            features = df_lngsb$Type,
            label = lang.iso(df_lngsb$lng),
            popup = lang.iso(df_lngsb$lng)
            )
```

##### Mapudungun (arn)
Mapudungun is an Araucanian language spoken by around 258 410 people.

The principal constructions expressing knowledge predication in the Mapudungun New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "arn"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Central Aymara (ayr)
Central Aymara is an Aymaran language spoken by around 1 464 100 people.

The principal constructions expressing knowledge predication in the Central Aymara New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "ayr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Carib (car)
Carib is a Cariban language spoken by around 8 558 people.

The principal constructions expressing knowledge predication in the Carib New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "car"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Cashibo-Cacataibo (cbr)
Cashibo-Cacataibo is a Pano-Tacanan language spoken by around 2 780 people.

The principal constructions expressing knowledge predication in the Cashibo-Cacataibo New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "cbr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Cuiba (cui)
Cuiba is a Guahiboan language spoken by around 2 640 people.

The principal constructions expressing knowledge predication in the Cuiba New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "cui"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### San Blas Kuna (cuk)
San Blas Kuna is a Chibchan language spoken by around 57 100 people.

The principal constructions expressing knowledge predication in the San Blas Kuna New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "cuk"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Culina (cul)
Culina is an Arawan language spoken by around 3 420 people.

The principal constructions expressing knowledge predication in the Culina New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "cul"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kotiria (gvc)
Kotiria is a Tucanoan language spoken by around 1 300 people.

The principal constructions expressing knowledge predication in the Kotiria New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "gvc"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Murui Huitoto (huu)
Murui Huitotois a Huitotoan language spoken by around 1000 people.

The principal constructions expressing knowledge predication in the Murui Huitoto New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "huu"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### San Andres Creole English (icr)
San Andres Creole English is an Indo-European>Germanic/Creole language spoken by around 12 000 people.

The principal constructions expressing knowledge predication in the San Andres Creole English New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "icr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kaiwá (kgk)
Kaiwá is a Tupian language spoken by around 18 000 people.

The principal constructions expressing knowledge predication in the Kaiwá New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kgk"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Southern Nambikuára (nab)
Southern Nambikuára is a Nambiquaran language spoken by around 720 people.

The principal constructions expressing knowledge predication in the Southern Nambikuára New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "nab"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Pilagá (plg)
Pilagá is a Guaicuruan language spoken by around 3490 people.

The principal constructions expressing knowledge predication in the Pilagá New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "plg"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Huallaga Huánuco Quechua (qub)
Huallaga Huánuco Quechua is a Quechuan language spoken by around 40 000 people.

The principal constructions expressing knowledge predication in the Huallaga Huánuco Quechua New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "qub"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Rikbaktsa (rkb)
Rikbaktsa is a Nuclear-Macro-Je language spoken by around 40 people.

The principal constructions expressing knowledge predication in the Rikbaktsa New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "rkb"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Epena (sja)
Epena is a Chocoan language spoken by around 3 500 people.

The principal constructions expressing knowledge predication in the Epena New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "sja"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Trinitario (trn)
Trinitario is an Arawakan language spoken by around 3 140 people.

The principal constructions expressing knowledge predication in the Trinitario New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "trn"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Sanumá (xsu)
Sanumá is a Yanomamic language spoken by around 6 000 people.

The principal constructions expressing knowledge predication in the Sanumá New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "xsu"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Yuracaré (yuz)
Yuracaré is an isolate language spoken by around 1 810 people.

The principal constructions expressing knowledge predication in the Yuracaré New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "yuz"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

### Africa
```{r}
df_lngsb <- df_lngs[which(df_lngs$area =="Africa"),]
map.feature(languages = lang.iso(df_lngsb$lng),
            features = df_lngsb$Type,
            label = lang.iso(df_lngsb$lng),
            popup = lang.iso(df_lngsb$lng)
            )
```

##### Afrikaans (afr)
Afrikaans is an Indo-European>Germanic language spoken by around 7 331 780 people.

The principal constructions expressing knowledge predication in the Afrikaans New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "afr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Hamer-Banna (amf)
Hamer-Banna is a South Omotic language spoken by around 26 900 people.

The principal constructions expressing knowledge predication in the Hamer-Banna New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "amf"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Zarma (dje)
Zarma is a Songhay language spoken by around 4 330 100 people.

The principal constructions expressing knowledge predication in the Zarma New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "dje"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Toro So Dogon (dts)
Toro So Dogon is a Dogon language spoken by around 50 000 people.

The principal constructions expressing knowledge predication in the Toro So Dogon New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "dts"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Igbo (ibo)
Igbo is a Atlantic-Congo>Volta-Congo>Benue-Congo>Igboid language spoken by around 29 000 000 people.

The principal constructions expressing knowledge predication in the Igbo New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "ibo"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Southern Kisi (kss)
Southern Kisi is a Atlantic-Congo>Mel language spoken by around 318 000 people.

The principal constructions expressing knowledge predication in the Southern Kisi New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kss"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Matal (mfh)
Matal is an Afro-Asiatic>Chadic language spoken by around 18 000 people.

The principal constructions expressing knowledge predication in the Matal New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mfh"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Ma'di (mhi)
Ma'di is a Central Sudanic language spoken by around 326 000 people.

The principal constructions expressing knowledge predication in the Ma'di New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mhi"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Moro (mor)
Moro is a Heibanic language spoken by around 72 000 people.

The principal constructions expressing knowledge predication in the Moro New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mor"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Murle (mur)
Murle is a Surmic language spoken by around 196 000 people.

The principal constructions expressing knowledge predication in the Murle New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mur"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Naro (nhr)
Naro is a Khoe-Kwadi language spoken by around 10 000 people.

The principal constructions expressing knowledge predication in the Naro New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "nhr"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Tamasheq (taq)
Tamasheq is an Afro-Asiatic>Berber language spoken by around 500 000 people.

The principal constructions expressing knowledge predication in the Tamasheq New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "taq"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Teso (teo)
Teso is a Nilotic language spoken by around 2 699 000 people.

The principal constructions expressing knowledge predication in the Teso New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "teo"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Uduk (udu)
Uduk is a Koman language spoken by around 22 000 people.

The principal constructions expressing knowledge predication in the Uduk New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "udu"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Wolaytta (wal)
Wolaytta is a Ta-Ne-Omotic language spoken by around 2 380 000 people.

The principal constructions expressing knowledge predication in the Wolaytta New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "wal"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Yalunka (yal)
Yalunka is a Mande language spoken by around 173 300 people.

The principal constructions expressing knowledge predication in the Yalunka New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "yal"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

### Eurasia
```{r}
df_lngsb <- df_lngs[which(df_lngs$area =="Eurasia"),]
map.feature(languages = lang.iso(df_lngsb$lng),
            features = df_lngsb$Type,
            label = lang.iso(df_lngsb$lng),
            popup = lang.iso(df_lngsb$lng)
            )
```

##### Modern Standard Arabic (arb)
Modern Standard Arabic is an Afro-Asiatic>Semitic language spoken by around 273 989 700 people.

The principal constructions expressing knowledge predication in the Modern Standard Arabic New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "arb"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Bengali (ben)
Bengali is an Indo-European>Indo-Iranian language spoken by around 228 651 040 people.

The principal constructions expressing knowledge predication in the Bengali New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "ben"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Car Nicobarese (caq)
Car Nicobarese is an Austroasiatic>Nicobaric language spoken by around 37 000 people.

The principal constructions expressing knowledge predication in the Car Nicobarese New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "caq"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Chechen (che)
Chechen is a Nakh-Daghestanian language spoken by around 1 526 650 people.

The principal constructions expressing knowledge predication in the Chechen New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "che"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Mandarin Chinese (cmn)
Mandarin Chinese is a Sino-Tibetan>Sinitic language spoken by around 921 233 120 people.

The principal constructions expressing knowledge predication in the Mandarin Chinese New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "cmn"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Dimasa (dis)
Dimasa is a Sino-Tibetan>Brahmaputran>Bodo-Garo language spoken by around 137 000 people.

The principal constructions expressing knowledge predication in the Dimasa New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "dis"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Middle English (enm)
Middle English was an Indo-European>Germanic language spoken in England around year 1000-1500.

The principal constructions expressing knowledge predication in the lngname? New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "enm"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

##### Basque (eus)
Basque is a isolate language spoken by around 537 860 people.

The principal constructions expressing knowledge predication in the Basque New Testament are shown in the table below.

```{r}
df_sub <- df[which(df$Language == "eus"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Hungarian (hun)
Hungarian is an Uralic language spoken by around 12 532 990 people.

The principal constructions expressing knowledge predication in the Hungarian New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "hun"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Iu Mien (ium)
Iu Mien is a Hmong-Mien language spoken by around 813 600 people.

The principal constructions expressing knowledge predication in the Iu Mien New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "ium"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Japanese (jpn)
Japanese is a Japonic language spoken by around 126 257 610 people.

The principal constructions expressing knowledge predication in the Japanese New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "jpn"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kannada (kan)
Kannada is a Dravidian language spoken by around 43 644 310 people.

The principal constructions expressing knowledge predication in the Kannada New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kan"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Halh Mongolian (khk)
Halh Mongolian is a Mongolic-Khitan language spoken by around 2 704 030 people.

The principal constructions expressing knowledge predication in the Halh Mongolian New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "khk"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Korean (kor)
Korean is a Koreanic language spoken by around 81 520 400 people.

The principal constructions expressing knowledge predication in the Korean New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kor"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Swedish (swe)
Swedish is an Indo-European>Germanic language spoken by around 9 654 400 people.

The principal constructions expressing knowledge predication in the Swedish New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "swe"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Thai (tha)
Thai is a Tai-Kadai language spoken by around 20 715 470 people.

The principal constructions expressing knowledge predication in the Thai New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "tha"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Turkish (tur)
Turkish is a Turkic language spoken by around 80 540 000 people.

The principal constructions expressing knowledge predication in the Turkish New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "tur"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

### Oceania
```{r}
df_lngsb <- df_lngs[which(df_lngs$area =="Oceania"),]
map.feature(languages = lang.iso(df_lngsb$lng),
            features = df_lngsb$Type,
            label = lang.iso(df_lngsb$lng),
            popup = lang.iso(df_lngsb$lng)
            )
```

##### Anggor (agg)
Anggor is a Senagi language spoken by around 1 270 people.

The principal constructions expressing knowledge predication in the Anggor New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "agg"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Bauzi (bvz)
Bauzi is a Geelvink Bay language spoken by around 1 350 people.

The principal constructions expressing knowledge predication in the Bauzi New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "bvz"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Daga (dgz)
Daga is a Dagan language spoken by around 9 000 people.

The principal constructions expressing knowledge predication in the Daga New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "dgz"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Fasu (faa)
Fasu is a Fasu language spoken by around 1 100 people.

The principal constructions expressing knowledge predication in the Fasu New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "faa"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kire (geb)
Kire is a Lower Sepik-Ramu language spoken by around 2 500 people.

The principal constructions expressing knowledge predication in the Kire New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "geb"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kalam (kmh)
Kalam is a Nuclear Trans New Guinea language spoken by around 20 000 people.

The principal constructions expressing knowledge predication in the Kalam New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kmh"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Doromu-Koki (kqc)
Doromu-Koki is a Manubaran language spoken by around 2 000 people.

The principal constructions expressing knowledge predication in the Doromu-Koki New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kqc"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kuot (kto)
Kuot is an isolate language spoken by around 1 500 people.

The principal constructions expressing knowledge predication in the Kuot New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "kto"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Meyah (mej)
Meyah is an East Bird's Head language spoken by around 14 800 people.

The principal constructions expressing knowledge predication in the Meyah New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "mej"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Wubuy (nuy)
Wubuy is a Gunwinyguan language spoken by around 280 people.

The principal constructions expressing knowledge predication in the Wubuy New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "nuy"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Olo (ong)
Olo is a Nuclear Torricelli language spoken by around 13 700 people.

The principal constructions expressing knowledge predication in the Olo New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "ong"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Rotokas (roo)
Rotokas is a North Bougainville language spoken by around 11 600 people.

The principal constructions expressing knowledge predication in the Rotokas New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "roo"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Kriol (rop)
Kriol is an English-lexifier Creole language spoken by around speakers 17 490 people.

The principal constructions expressing knowledge predication in the Kriol New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "rop"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

##### Tabaru (tby)
Tabaru is a North Halmahera language spoken by around 15 000 people.

The principal constructions expressing knowledge predication in the Tabaru New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "tby"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### North Tanna (tnn)
North Tanna is an Austronesian>Malayo-Polynesian language spoken by around 5000 people.

The principal constructions expressing knowledge predication in the North Tanna New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "tnn"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Warlpiri (wbp)
Warlpiri is a Pama-Nyungan language spoken by around 2300 people.

The principal constructions expressing knowledge predication in the Warlpiri New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "wbp"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```
##### Yele (yle)
Yele is an isolate language spoken by around 5000 people.

The principal constructions expressing knowledge predication in the Yele New Testament are shown in the table below.
```{r}
df_sub <- df[which(df$Language == "yle"), c("Construction", "Gloss", "Ocurrences", "EtymNotes", "UsageNotes", "Notes")]
datatable(data = df_sub, rownames = F)
```

### Download
<a href="constructions.csv" download>Download the full list of constructions</a>
