---
title: "Knowledge Predication - Online Supplementary Materials"
output:
  html_document:
    theme: paper
    include:
      after_body: footer.html
    toc: true
    toc_depth: 5
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, echo=FALSE}
library(DT)
library(tidyverse)
library(lingtypology)
library(knitr)
```


This site contains supplementary materials to my dissertation **Knowledge predication - A semantic typology** which is available <a href="https://su.diva-portal.org/smash/record.jsf?dswid=-269&pid=diva2%3A1800727&c=18&searchType=SIMPLE&language=sv&query=anna+sj%C3%B6berg&af=%5B%5D&aq=%5B%5B%5D%5D&aq2=%5B%5B%5D%5D&aqe=%5B%5D&noOfRows=50&sortOrder=author_sort_asc&sortOrder2=title_sort_asc&onlyFullText=false&sf=all">here</a> 

The site contains:

- the <a href="clusters.html">full clustering</a> of the cognition-perception-ability verses analysed, presented in chapter 5 of *Knowledge predication*
- the <a href="dimensions.html">location of the verses</a> on the six analysed dimensions fo CMDS analysis presented in chapter 7
- the <a href="markers.html">markers</a> correlated with these dimensions, discussed in chapter 9

---

### Sample

*Knowledge predication* builds on an 83-languages variety sample.

```{r, include=FALSE, echo=FALSE}
df <- read.csv("languages.csv", sep=";")
```


```{r, echo=FALSE}
map.feature(languages = lang.iso(df$lng),
            features = df$Type,
            label = lang.iso(df$lng),
            popup = lang.iso(df$lng)
            )

```







