---
title: "Markers associated with the dimensions of knowledge predication"
output: 
  html_document:
    theme: paper
    include:
      after_body: footer.html
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE, echo=FALSE}
library(DT)
library(lingtypology)
knitr::opts_chunk$set(echo = FALSE)
df <- read.csv("pointbiserial_stems.csv", header=T, sep="\t", encoding="UTF-8")
df$Language <- lang.iso(df$Language)
df$P <- round(df$P, 4)
df$R <- round(df$R, 2)
df <- df[,c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Dimension", "Combinations")]
```

### Constructional Dimension 1
The tables below show the markers correlated with Constructional Dimension 1, i.e. the first dimension of a CMDS analysis of a distance measure based only on *constructional markers*. First, the markers *positively* correlated with Constructional Dimension 1 are given. In section 9.3.2. of *Knowledge predication* I analyse these as being related to *achievement meaning*. This is followed by markers *negatively* correlated with Constructional Dimension 1, which I analyse as being related to *state meaning*. 

#### Markers positively  correlated with Constructional Dimension 1

##### Lexical markers
```{r}
df1 <- df[which((df$Dimension=="Dim1cx") & (df$R > 0)),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df1)

```
##### Constructional markers

#### Markers negatively correlated with Constructional Dimension 1
```{r}
df2 <- df[which((df$Dimension=="Dim1cx") & (df$R < 0)),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df2)

```

### Lexical Dimension 1
***Under construction***

```{r}
df3 <- df[which((df$Dimension=="Dim1lex")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df3)

```

### Dimension 2
***Under construction***

```{r}
df4 <- df[which((df$Dimension=="Dim2")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df4)

```

### Dimension 3

***Under construction***
```{r}
df5 <- df[which((df$Dimension=="Dim3")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df5)

```
### Dimension 4

***Under construction***
```{r}
df6 <- df[which((df$Dimension=="Dim4")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df6)

```
### Dimension 5

***Under construction***
```{r}
df7 <- df[which((df$Dimension=="Dim5")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df7)

```
### Dimension 6

***Under construction***
```{r}
df8 <- df[which((df$Dimension=="Dim6")),c("Construction", "Language", "Ocurrences", "R", "P", "Connections", "Combinations")]
datatable(data = df8)

```